Pyg4ometry: a python library for the creation of Monte Carlo particle transport physical geometries

### 2019-08-11 public/paper/pyg4ometry.tex
Code for registry merge

\subsection{Geant Detector Mark-up Language} 
To exchange geometry descriptions Geant Detector Mark-up Language (GDML) was developed. Geant4 and ROOT can read and write GDML format and it is commonly
used as an exchange format for Geant4 geometries. 
\begin{table}[hbt!]
\centering
\begin{tabular}{|c|c|c|} \hline
GDML tag 		&  Child tags				& pyg4ometry class 			\\ \hline
Defines 			&						&						\\
Solids 			&						&						\\
Materials 			&						&						\\
Structure			&						&						\\ \hline
\end{tabular}
\caption{GDML tags and corresponding {\it pyg4ometry} classes.}
\end{table}

\section{{\em pyg4ometry} design and layout}
The core of {\em pyg4ometry} consists of python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
The constructors of the python classes are kept as close to the original Geant4 C++ implementation so that {\it pyg4ometry} users do not have to learn 
a new API. Geometry construction in python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
should be able to start creating geometry in pyg4ometry immediately. In the following sections novel or important developments in {\it pyg4ometry} are described.

>>>>

\subsection{Geant Detector Mark-up Language} 
To exchange geometry descriptions Geant Detector Mark-up Language (GDML) was developed. Geant4 and ROOT can read and write GDML format and it is commonly
used as an exchange format for Geant4 geometries. 
\begin{table}[hbt!]
\centering
\begin{tabular}{|l|l|l|} \hline
GDML tag 		&  Child tags				& pyg4ometry class 				\\ \hline
define 			& constant				& gdml.Constant				\\
				& variable					& gdml.Variable					\\
				& quantity					& gdml.Quantity				\\
				& expression 				& gdml.Expression				\\
				& position					& gdml.Position					\\
				& rotation					& gdml.Rotation				\\
				& scale					& gdml.Scale					\\
				& matrix					& gdml.Matrix					\\
materials 			& element					& geant4.Element				\\
				& isotope					& geant4.Isotope				\\
				& material					& geant4.Material				\\
solid  			& box					& geant4.solid.Box				\\
	  			& tube					&							\\
	  			& cutTube					&							\\
	  			& cone					&							\\
	  			& para					&							\\
	  			& trd						&							\\
	  			& trap					&							\\
	  			& sphere					&							\\
	  			& orb					&							\\
	  			& torus					&							\\
	  			& polycone				&							\\
	  			& genericPolycone			&							\\
	  			& polyhedra				&							\\
	  			& eltube					&							\\
	  			& ellipsoid					&							\\
	  			& elcone					&							\\
				& paraboloid				&							\\
				& hype					& 							\\
				& tet						& 							\\
				& xtru					& 							\\
				& twistedbox				& 							\\
				& twistedtrap				& 							\\
				& twistedtrd				& 							\\
				& twistedtube				& 							\\
				& arb8					& 							\\
				& tesselated				& 							\\
				& union					& 							\\
				& subtraction				& 							\\
				& intersection				& 							\\
				& multiUnion				& 							\\				
	  			& opticalsurface			&							\\
structure			& volume					& geant4.LogicalVolume			\\
				& physvol					& geant4.PhysicalVolume			\\ 
				& replicavol				& geant4.ReplicaVolume			\\ 
				& paravol					& geant4.ParameterisedVolume	\\ 
				& divisionvol				& geant4.DivisionVolume			\\
				& skinsurface				& geant4.SkinSurface			\\ 
				& bordersurface			& geant4.BorderSurface			\\ \hline

\end{tabular}
\caption{GDML tags and corresponding pyg4ometry classes.}
\end{table}

\section{pyg4ometry design and layout}
The core of {\em pyg4ometry} consists of python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
The constructors of the python classes are kept as close to the original Geant4 C++ implementation so that {\it pyg4ometry} users do not have to learn 
a new API. Geometry construction in python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
should be able to start creating geometry in pyg4ometry immediately. In the following sections novel or important developments in {\it pyg4ometry} are described.
